COMPAS Race Analysis

### 2022-04-05 final_metrics_analysis.Rmd

from aif360.sklearn.preprocessing import ReweighingMeta
from aif360.sklearn.inprocessing import AdversarialDebiasing
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta
from aif360.sklearn.metrics import disparate_impact_ratio, average_odds_error, generalized_fpr, average_odds_difference
from aif360.sklearn.metrics import generalized_fnr, difference, statistical_parity_difference, equal_opportunity_difference, generalized_entropy_error

@@

@@

@@

#bt_grp_gen_entr_error = between_group_generalized_entropy_error(y_test, y_pred, alpha=1, pos_label = 0)

#print(f'[Baseline] The between group generalized entropy error is {bt_grp_gen_entr_error: .2}')

>>>>

from aif360.sklearn.preprocessing import ReweighingMeta
from aif360.sklearn.inprocessing import AdversarialDebiasing
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta

from aif360.sklearn.metrics import disparate_impact_ratio, average_odds_difference, statistical_parity_difference, equal_opportunity_difference
from aif360.sklearn.metrics import generalized_entropy_error, generalized_entropy_index, theil_index, consistency_score

@@

**add brief definition of group fairness**

@@

This metric is the ratio of how often the favorable outcome occurs in one group versus the other. In the case of recidivism, this is the ratio of how many white defendants are predicted to not recidivate compared to how many black defendants are predicted to not recidivate.

A value of 1 means that the ratio is exactly 1:1. Less than 1 means the privileged group (white defendants) benefits, while a value greater than 1 means the unprivileged group (Black defendants) benefits. According to AI Fairness 360, a ratio between .8 to 1.25 is considered fair.

The disparate impact ratio is calculated with the formula:

@@
